---
title: "Sankey Plots - Flow Network "
author: "Leonardo Martins"
date: "22 de janeiro de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 10
    fig_width: 9
    highlight: tango
    keep_md: yes
    theme: flatly
    toc: yes
---

Here you can find a first a draft of Sankey Graphs for Website Flow Pages - This report was based on LWT data sent from Felipe in 2015. 

####Results: [http://rpubs.com/leomartinsjf/SankeyLWT]

####Git: [https://github.com/leomartinsjf/SankeyLWT]

####################################
#Sankey Plots from Adjacency Matrix#
####################################

```{r message=FALSE}
#If you don't have these packages installed use:
#install.packages("igraph")
#install.packages("networkD3")
#install.packages("curl")

require(igraph) #load package for social network analysis
require(networkD3) #load package for sankey network
require(curl) #load package to download csv files


#In order to change the Sankey plot configuration - please, acesses  "~/Library/Frameworks/R.framework/Versions/"your version 3.xxx"/library/networwD3/htmlwidgets/lib/sankey.js

# This current version was made using the following sankey.js "https://dl.dropboxusercontent.com/s/5386z4jwrymlubq/sankey.js"
```


#####################
#Data manipulation  #
#####################
```{r}
#Raw Data sent from Felipe April 2015
#https://dl.dropboxusercontent.com/s/2y9dl246ctv9y59/result-2.txt
#I had to manipulated this data on Excel in order to create a csv file with labels and another one with the squared matrix

data <- read.csv(curl("https://dl.dropboxusercontent.com/s/dz571ak1whb8lqd/grafo.csv"), sep = ";")
#Importing  bi-directional squared matrix with labels into a "data" object

matrix=as.matrix(data)
#Transforming dataframe into a "matrix" adjacency with

colnames(matrix)<-c(0:40)
#Coding matrix coluns as numeric labels 

label <- read.csv(curl("https://dl.dropboxusercontent.com/s/erdu802n7bsqk5e/label.csv"), sep=";")
#Importing original labels - page adress

Nodes <- as.data.frame(label$Label)
#Generating nodes object with orderd labels

colnames(Nodes)<- as.factor(colnames(Nodes))
#Setting column names 
```


################################################################
#Preparing First Sankey Draft - With Loops and Recursive Paths #
################################################################
```{r}
network1=graph_from_adjacency_matrix(matrix,mode="directed",weighted=T,diag=T)
#Generating a graph network structure - overall flow - directed with weights and diag different from zero

Links1 <- get.data.frame(network1)
#Getting a dataframe from igraph object (from, to, weight) - overall flow

Links1$logweight <- log(Links1$weight)
#Creating a transformed variable using log weight

Links1$from<-as.numeric(Links1$from)
#Converting to numeric

Links1$to<-as.numeric(Links1$to)
#Converting to numeric

#Generating first sankey plot object
#sankeyNetwork(Links= Links1, Nodes = Nodes, Source = 'from', Target = 'to', Value = 'logweight', NodeID ="label$Label", fontSize=12, nodeWidth=30)

#This is not included as we need to check the Java Scrisct template for Sankey Plot with Recursive Patterns
```

##############################################################################
#Preparing Second Sankey - No Loops and non Recursive - Forced Directed Paths #
##############################################################################
```{r}
network2=graph_from_adjacency_matrix(matrix,mode="undirected",weighted=T,diag=F)
#Generating a igraph network structure - directed flow without loops - undirected with weight and diag equal to zero - only the upper matrix triangle it is used 

#IMPORTANT: Hopefully this is the right one to show forward flow  - if it is not the case use the following network object
#network2=graph_from_adjacency_matrix(matrix,mode="lower",weighted=TRUE,diag=F)

Links2 <- get.data.frame(network2)
#Getting a dataframe from igraph object (from, to, weight)  - directed flow without loops

Links2$logweight <- log(Links2$weight)
#Creating a transformed variable using log weight

Links2$from<-as.numeric(Links2$from)
#Converting to numeric

Links2$to<-as.numeric(Links2$to)
#Converting to numeric

#Generating sankey plot object
sankeyNetwork(Links= Links2, Nodes = Nodes, Source = 'from', Target = 'to', Value = 'logweight', NodeID ="label$Label", fontSize=12, nodeWidth=5)
```

#############################################################################
#Time to be "lazy" - Creating functions to replicated the sankey plots above# 
#############################################################################

#1 - Function to generate a sankey plot including foward and backward flow links
```{r}
sankeyFT <- function(x, y) {
a <- y[(y$from %in% c(x)|y$to %in% c(x)),]
a1<-cat("#Links Forward (From) and Backward (To),\n")
sankeyNetwork(Links= a, Nodes = Nodes, Source = 'from', Target = 'to', Value = 'logweight', NodeID ="label$Label", fontSize=12, nodeWidth=30)
}
```

#2 - Function to generate a sankey plot including only foward links (From)
```{r}
sankeyF <- function(x, y) {
b <- y[y$from %in% c(x),]
b1<-cat("#Links From - no log transformation due to low level of observations\n")
sankeyNetwork(Links= b, Nodes = Nodes, Source = 'from', Target = 'to', Value = 'logweight', NodeID ="label$Label", fontSize=12, nodeWidth=30)
}
```

#3 - Function to generate a sankey plot including only backward links (To)
```{r}
sankeyT <- function(x, y) {
c <- y[y$to %in% c(x),]
c1<-cat("#Links To  - no log transformation due to low level of observations\n")
sankeyNetwork(Links= c, Nodes = Nodes, Source = 'from', Target = 'to', Value = 'logweight', NodeID ="label$Label", fontSize=12, nodeWidth=30)
}
```

##############################################################
#Organizing Plots by Interaction with Specific Section Pages #
##############################################################

########################################
##Zero "Frontpage" (1:3;15;27;32;39)#
########################################

Selecting links made by at least one node from Zero Step (Frontpages) 

########################################
###1 Model With Loops and Recursive Paths#
########################################
```{r}
#sankeyFT(c(1:3,15,27,32:39),Links1)
#sankeyF(c(1:3,15,27,32:39), Links1)
#sankeyT(c(1:3,15,27,32:39), Links1)

#These plots are not included as we need to check the Java Scrisct template for Sankey Plot with Recursive Patterns
```

###########################################
###2 Model Without Loops or Recursive Paths#
###########################################

```{r}
sankeyFT(c(1:3,15,27,32:39),Links2)
sankeyF(c(1:3,15,27,32:39), Links2)
sankeyT(c(1:3,15,27,32:39), Links2)
```

#####################################################
##First Step "Preparando-parar-de-fumar" (V16 to V26)#
#####################################################

Selecting links made by at least one node from First Step 

########################################
###1 Model With Loops and Recursive Paths#
########################################

```{r}
#sankeyFT(c(16:26),Links1)
#sankeyF(c(16:26), Links1)
#sankeyT(c(16:26), Links1)

#These plots are not included as we need to check the Java Scrisct template for Sankey Plot with Recursive Patterns
```
###########################################
###2 Model Without Loops or Recursive Paths#
###########################################

```{r}
sankeyFT(c(16:26),Links2)
sankeyF(c(16:26), Links2)
sankeyT(c(16:26), Links2)
```

#####################################################
##Second Step "Pronto-para-parar-de-fumar" (V4 to 14)#
#####################################################

Selecting links made by at least one node from First Step 

########################################
###1 Model With Loops and Recursive Paths#
########################################
```{r}
#sankeyFT(c(4:14),Links1)
#sankeyF(c(4:14), Links1)
#sankeyT(c(4:14), Links1)

#These plots are not included as we need to check the Java Scrisct template for Sankey Plot with Recursive Patterns
```

###########################################
###2 Model Without Loops or Recursive Paths#
###########################################
```{r}
sankeyFT(c(4:14),Links2)
sankeyF(c(4:14), Links2)
sankeyT(c(4:14), Links2)
```

########################################
##Third Step "Parou-de-Fumar" (V28 to 31)#
########################################

Selecting links made by at least one node from First Step 

########################################
###1 Model With Loops and Recursive Paths#
########################################

```{r}
#sankeyFT(c(28:38),Links1)
#sankeyF(c(28:38), Links1)
#sankeyT(c(28:38), Links1)

#These plots are not included as we need to check the Java Scrisct template for Sankey Plot with Recursive Patterns
```

###########################################
###2 Model Without Loops or Recursive Paths#
###########################################

```{r}
sankeyFT(c(28:38),Links2)
sankeyF(c(28:38), Links2)
sankeyT(c(28:38), Links2)
```